---
title: "From_Phyloseq_to_Biom"
author: "roshan padmanabhan"
date: "February 20, 2018"
output: html_document
---

Aim : to convert the phyloseq object to biom
- steps include saving the phyloseq object into OTU, TAXA and METADATA files
- and join them by biom convert  which conver it to json biom object

```{r}
source("~/bin/metagenomics_fns.R")
```


```{r}
load("Joined_TA_A.phyloseq")
```

```{r}
joined_ps
```

```{r}
mg.table_denovo_and_gg( joined_ps )
```
Note :
------
- Not removing the DENOVO OTUs

```{r}
# ps = mg.prune_taxa( joined_ps, "DENOVO", rev_search = T )
```

```{r}
otu_fn ="otu.tsv"
tax_fn = "tax.tsv"
map_fn = "map.tsv"
```

Save OTU
```{r}
write.table( otu_table(joined_ps), file = otu_fn, row.names = T, quote = F, sep="\t" )
```

Save TAX table
```{r}
tx = data.frame( tax_table(joined_ps  ) )
#tx2 = tx %>% dplyr::mutate( taxonomy = paste0( Kingom ,'; ', Phylum,"; ",Class,"; ",Order,"; ",Family,"; ",Genus,"; ",Species ) ) %>% dplyr::select( taxonomy )
#rownames( tx2 ) = rownames( tx )
write.table( tx, file=tax_fn, row.names=T , quote=F, sep="; 
             ")
```

Save Metadata
```{r}
mapx = data.frame(sample_data(  joined_ps    ))
```

```{r}
colnames(mapx)
```

```{r}
mapy = mapx %>% dplyr::select( SAMPLE, Ethnicity,Group,Pulse,DBP,SBP,HLD,Description,HTN,BMI,CurrentAge,Sex,Age_at_Proc,Aspirin,SAMPLE,TISSUE ) %>% 
  dplyr::rename("#SampleID" = SAMPLE) 
```

```{r}
write.table( mapy, file=map_fn, row.names=T , quote=F, sep="\t")
```


Most IMP.
- I manually edited TAXA 
- added #OTU ID taxonomy as the first column
- should have put it on the TAXA
- manually edited otu.tsv added #OTU ID for the index column

Make Biom 
```{r}
system( "biom convert -i otu.tsv -o otu.j.biom --to-json --table-type 'OTU table' --sample-metadata-fp map.tsv" )
system( "biom add-metadata -i otu.j.biom -o otu.wt.j.biom --output-as-json --observation-metadata-fp tax.tsv" )
```

