---
title: "Merging_Phyloseq.R"
author: "Roshan Padmanabhan"
date: "2/9/2018"
output: html_document
---
Objective
=========
- Merge the A and TA phyloseq object
- Problems are these two phyloseq objects are of different dimensions
  - ie. differet number of samples , 
  - different mapping files but some variables are same in both 

```{r}
source("~/bin/metagenomics_fns.R")
```

Phyloseq Objects
================
```{r}
load("A/A_filtered_ps2.phyloseq")
A_ps2 = ps2
```

```{r}
load("TA/TA_filtered_ps2.phyloseq")
TA_ps2 = ps2
```

```{r}
A_ps2
```

```{r}
TA_ps2
```

Lets split the phyloseq objects
-------------------------------
Tree
-------
```{r}
A_TRE = phy_tree(A_ps2)
TA_TRE = phy_tree( TA_ps2)
```

OTUS
--------
- fixing rownames
```{r}
TA_OTU = as.data.frame(otu_table(TA_ps2))
A_OTU = as.data.frame(otu_table(A_ps2))
TA_OTU$OTU = rownames(TA_OTU)
rownames(TA_OTU) = NULL
A_OTU$OTU = rownames(A_OTU)
rownames( A_OTU) = NULL
class(TA_OTU)
class(A_OTU)
```
TAXA
--------
```{r}
TA_TAX = as.data.frame( tax_table( TA_ps2 ) )
A_TAX = as.data.frame( tax_table( A_ps2 ) )
TA_TAX$OTU = rownames(TA_TAX)
rownames(TA_TAX) = NULL
A_TAX$OTU = rownames(A_TAX)
rownames( A_TAX) = NULL
class(TA_TAX)
class(A_TAX)
```
MAP
--------
```{r}
TA_MAP = data.frame(sample_data( TA_ps2))
A_MAP = data.frame(sample_data(A_ps2))

A_MAP$SAMPLE = rownames( A_MAP )
rownames(A_MAP) = NULL
TA_MAP$SAMPLE = rownames( TA_MAP )
rownames(TA_MAP) = NULL
# add a new variable tissue A : Aorta and TA : Temporal Artery
A_MAP$TISSUE = "A"
TA_MAP$TISSUE = "TA"

```


Merging OTU tables of TA and A
------------------------------
- expecting interset of OTUs rows ie 788  and 49 + 43 ( 92 ) columns
- rest fill with 0's

```{r}
intersect(A_OTU$OTU ,TA_OTU$OTU) %>% len()
```

```{r}
joined_OTU = inner_join(A_OTU ,TA_OTU, by='OTU')
rownames(joined_OTU) = joined_OTU$OTU
joined_OTU$OTU = NULL
```

Merging TAX tables of TA and A
------------------------------
- expecting interset of OTUs rows ie 788  and 49 + 43 ( 92 ) columns
- rest fill with 0's
```{r}
intersect(A_TAX$OTU ,TA_TAX$OTU) %>% len()
```
```{r}
joined_TAX = merge(A_TAX, TA_TAX ) 
rownames(joined_TAX) = joined_TAX$OTU
joined_TAX$OTU = NULL
joined_TAX %>% dim
```

Merging MAP of TA and A
-----------------------
- only 13 variables are common between TA and A
```{r}
A_MAP %>% dim()
TA_MAP %>% dim()
```
```{r}
intersect(colnames(A_MAP), colnames(TA_MAP))
```
```{r}
union(colnames(A_MAP), colnames(TA_MAP))
```
- so im expecting 92 rows (sample ids) and 13 + 1 columns of variables
```{r}
joined_MAP = full_join(A_MAP, TA_MAP, by=intersect(colnames(A_MAP), colnames(TA_MAP))) %>% dplyr::select( intersect(colnames(A_MAP), colnames(TA_MAP)) )
rownames( joined_MAP ) = joined_MAP$SAMPLE
```

```{r}
sort_otu_names =  sort( rownames(joined_OTU) )
joined_OTU = joined_OTU[sort_otu_names,]
joined_TAX = joined_TAX[sort_otu_names,]
```

```{r}
#joined_TAX2 = joined_TAX %>% dplyr::mutate( 'taxonomy' = paste0( Kingom,"; ",Phylum,"; ",Class,"; ",Order,"; ",Family,"; ",Genus,"; ",Species)) %>% dplyr::select(taxonomy)
joined_TAX2 = joined_TAX
rownames(joined_TAX2 )  = rownames(joined_TAX )

```

Make a new phyloseq object
--------------------------
```{r}
joined_OTU_t = otu_table(joined_OTU, taxa_are_rows = TRUE)
```

```{r}
joined_TAX_t = tax_table( as.matrix( joined_TAX2 ) )
```

```{r}
joined_MAP_t = sample_data( joined_MAP)
```

Voilà I Made a new phyloseq object
--------------------------
```{r}
joined_ps = phyloseq(joined_OTU_t,joined_TAX_t, joined_MAP_t , A_TRE)
```

```{r}
joined_ps
```
```{r}
sample_variables(joined_ps)
```


Make Some Ordination Plots
===========================
- f**kin ape throws error 
- no wunifrac
```{r}
Vas_ord_u = phyloseq::ordinate(joined_ps, "PCoA", distance="unifrac")
#Vas_ord_wu = phyloseq::ordinate(joined_ps, "PCoA", distance="wunifrac")
Vas_ord_b = phyloseq::ordinate(joined_ps, "PCoA", distance="bray")
```

PCoA with Bray [ Tissue & Group ]
------------------
```{r}
p1 =plot_ordination(joined_ps, Vas_ord_b, type="sample", color="TISSUE", shape="Group" ,title="Ordination Plot::BC::Vasculitis samples") 
p1 = p1 + theme_pubr() + theme(legend.position = "right")+ geom_point(size=3, alpha=0.75)
p1 = p1+ geom_vline(xintercept = 0.0) + geom_hline(yintercept = 0.0)
p1
```


PCoA with Bray [ Tissue & Group ]
------------------
```{r}
p1 =plot_ordination(joined_ps, Vas_ord_b, type="sample", color="Group", shape="TISSUE" ,title="Ordination Plot::BC::Vasculitis samples") 
p1 = p1 + theme_pubr() + theme(legend.position = "right")+ geom_point(size=3, alpha=0.75)
p1 = p1+ geom_vline(xintercept = 0.0) + geom_hline(yintercept = 0.0)
p1
```

PCoA with BC [ Tissue ]
-------------------
```{r}
p1 =plot_ordination(joined_ps, Vas_ord_b, type="sample", color="TISSUE",title="Ordination Plot::U::Vasculitis samples") 
p1 = p1 + theme_pubr() + theme(legend.position = "right") + geom_point(size=2, alpha=0.75)
p1 = p1+ geom_vline(xintercept = 0.0) + geom_hline(yintercept = 0.0)
p1
```




PCoA with Unifrac Distance [ Tissue & Group ]
---------------------------------------------
```{r}
p1 =plot_ordination(joined_ps, Vas_ord_u, type="sample", color="TISSUE", shape="Group" ,title="Ordination Plot::U::Vasculitis samples") 
p1 = p1 + theme_pubr() + theme(legend.position = "right") + geom_point(size=3, alpha=0.75)
p1 = p1+ geom_vline(xintercept = 0.0) + geom_hline(yintercept = 0.0)
p1
```


PCoA with Unifrac Distance [ Tissue & Group ]
-------------------
```{r}
p1 =plot_ordination(joined_ps, Vas_ord_u, type="sample", color="Group", shape="TISSUE" ,title="Ordination Plot::U::Vasculitis samples") 
p1 = p1 + theme_pubr() + theme(legend.position = "right") + geom_point(size=3, alpha=0.75)
p1 = p1+ geom_vline(xintercept = 0.0) + geom_hline(yintercept = 0.0)
p1
```

PCoA with Unifrac Distance [ Tissue ]
-------------------
```{r}
p1 =plot_ordination(joined_ps, Vas_ord_u, type="sample", color="TISSUE",title="Ordination Plot::U::Vasculitis samples") 
p1 = p1 + theme_pubr() + theme(legend.position = "right") + geom_point(size=3, alpha=0.75)
p1 = p1+ geom_vline(xintercept = 0.0) + geom_hline(yintercept = 0.0) 
p1
```


```{r}
save(joined_ps, file="Joined_TA_A.phyloseq")
```









